Make any stupid plot you want

### 2020-12-21 draft/sections/math.tex
fleshing out p

 is mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to pixel space. For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, r, g, b, a\}
    \label{eq:rho}
\end{equation}

@@

\begin{figure}[h]
    \includegraphics[width=.4\linewidth]{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

with fiber $P$ that encodes visual paramters such as position or color. As in section~\ref{sec:data_fiber}, the fields in $P$ are strongly typed. The function $\nu: E \rightarrow V$ maps from data space to visual space  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"] & V \arrow[ld, "\pi"'] \\
        K                                    &                     
        \end{tikzcd}
\end{equation}

such that the visual section $\mu: K \rightarrow V$ 
\begin{equation}
    \begin{tikzcd}
        E \arrow[r, "\nu"]                      & V \\
        K \arrow[ru, "\mu"'] \arrow[u, "\tau"'] &  
        \end{tikzcd}

\end{equation}

where visual transformers $\nu$ applied to data $\tau$ is equivalent to $\mu$ such that $\mu(k) = \nu\circ\tau(k)$. To obtain the equivalent visual values in screen space $S$, the look up map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}
such that when $\xi(s) = k$, there is a mapping from screen space to k  $\xi^*\tau(s) = \tau(k)$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "Q"] \arrow[rd, "\xi^*\pi"'] & H \arrow[d, "\pi"] \\
                                                      & S                 
    \end{tikzcd}
\end{equation}
the function $Q:\xi^*V\rightarrow H$ composites points in $V$ into $\mathbb{R^7}$ tuples. The section $\mu$ is pulled over $s$

@@

such that the composition $Q$ of $\mu$ is equivalent to the render $\rho(s) = Q\circ\mu(s)$. The full visualization path is
\begin{equation} 
    \begin{tikzcd}
        E \arrow[r, "\nu=transforms"] & V                                                              & \xi^*V \arrow[r, "Q = \text{set attrs}"]                             & H \\
                                  & K \arrow[lu, "\tau = data"] \arrow[u, "{\mu = \{\tau,\nu\}}"'] & S \arrow[l, "\xi - init?draw"] \arrow[u, "\xi^*\mu = \nu\circ\tau"'] &  
    \end{tikzcd}
\end{equation}

\subsubsection{Compositing}

$Q$ is the assembly function for the visual idiom step something something something something something

\subsubsection{Channels}

%% the \mu [oeve gpes here maybe]
Each $\nu$ function maps a field $\tau_c$ to a paramterized visual field $\mu$, for example the color or shape visual channels \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. The set of $\nu$ is a functor from data to visual space such that any $\nu$ is an equivariant map if

\begin{equation}
    \begin{tikzcd}
        E_1 \arrow[r, "F" description] \arrow[d, "" description] & V_1 \arrow[d, "f" description] \\
        E_2 \arrow[r, "F" description]                            & V_2                           
    \end{tikzcd}
\end{equation}

$E$ or $J(E)$
%nu is functor
% examples of nu \tau\mu pairs - ordinal
%maybe param is the wrong thing 
Define a channel in terms of nus
This is what we mean by equivariance: 
step thrpoughh measurment scale groups
doesn't matter where computation lives

Here is the thing you need to preserve for {X} when writing a transform:

compose $\nu_{param}$ visual characteristic mappers
\begin{equation}
    \nu(\tau) = \mu
\end{equation}
where $\tau_{param}$ is a field in $\tau$ bound to the paremeter and $\mu_param$ is an intermediate visual representation such that $\nu_shape(\tau_shape)$ returns a $\mu_shape$ function that returns a shape for each $k$.

%For example, given a categorical field $c$ carry through temperature, maybe picture?

$\nu$ is Hom set? 
1) must have identity
2) is composable
3) associativity

homomorphism in land of categories:
objects in C, objects in D
C arrow D
 A-B for example stephens group scale

every $\nu$ is a functor that

put all the functorial things together is still functorial 
%argument into  is $\[\nu_{0}(\tau_{0}), \ldots \nu_{n}(\tau_{n})\]$

% complex columns are combined to \nu

%% \nu is structure preserving if  E->E  & H->H under nu. \phi can be one of the scales in Stevens

% concrete example of \nu as one of our encodings, if artist is faithfully preserving 
% if was fiber, trans on fiber bundle. we require that nu goes to visual side that can support same translation  - work through some examples : if an artist wanted to preserve, this is what it would have to do - for example relations, interval

%%The measurement spaces $X$ are each variables and have the properties of measurement scales, such as Steven's nominal, ordinal, interval, and ratio \cite{stevensTheoryScalesMeasurement1946}. Stevens talks about measurements and this is how we define it here:.... can check symmatry under stevens via carry through on tau

 Can in theory approximate hatching/dashing/etc can be approximated w/ functions and neighborhood of k.

>>>>

 is mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to pixel space.

 \subsubsection{Section $\rho$}
 For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, r, g, b, a\}
    \label{eq:rho}
\end{equation}

@@

\subsubsection{{Example}}
\begin{figure}[h]
    \includegraphics[width=.4\linewidth]{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

with fiber $P$ that encodes visual paramters such as position or color. As in section~\ref{sec:data_fiber}, the fields in $P$ are strongly typed. Inside the artist is also the equivalance class map $\xi: S \rightarrow K$ that goes from a region $s$ to its associated point $k$
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}
such that when $\xi(s) = k$, $\xi^*\tau(s) = \tau(k)$.

\subsubsection{Visual Mapping}

The function $\nu: E \rightarrow V$ maps from data space to visual space  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"] & V \arrow[ld, "\pi"'] \\
        K                                    &                     
        \end{tikzcd}
\end{equation}

such that the visual section $\mu: K \rightarrow V$  is equivalent to the visual transformation of the data $\mu(k) = \nu\circ\tau(k)$
\begin{equation}
    \begin{tikzcd}
        E \arrow[r, "\nu"]                      & V \\
        K \arrow[ru, "\mu"'] \arrow[u, "\tau"'] &  
        \end{tikzcd}
\end{equation}

The constraint on $\nu: \tau\rightarrow \mu$ is that $\tau$ and $\mu$ must be equivariant.

%%set up proofs here

\subsubsection{Visual Composition}
The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "Q"] \arrow[rd, "\xi^*\pi"'] & H \arrow[d, "\pi"] \\
                                                      & S                 
    \end{tikzcd}
\end{equation}
the function $Q:\xi^*V\rightarrow H$ composites points in $V$ into $\mathbb{R^7}$ tuples. The section $\mu$ is pulled over $s$

@@

such that the composition $Q$ of $\mu$ is equivalent to the render $\rho(s) = Q\circ\mu(s)$.

\subsubsection{Pipeline}
The full visualization path is
\begin{equation} 
    \begin{tikzcd}
        E \arrow[r, "\nu=transforms"] & V                                                              & \xi^*V \arrow[r, "Q = \text{set attrs}"]                             & H \\
                                  & K \arrow[lu, "\tau = data"] \arrow[u, "{\mu = \{\tau,\nu\}}"'] & S \arrow[l, "\xi - init?draw"] \arrow[u, "\xi^*\mu = \nu\circ\tau"'] &  
    \end{tikzcd}
\end{equation}
